---
title: "Workload Report"
output:
  html_document:
    df_print: paged
    toc: true
  pdf_document:
    fig_width: 7
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: yes
params:
  dept: "AFST"
  term: 202410
  faculty:
  fac_list: 1
  tables: 1
---

```{r setup, include=FALSE,  fig.width = 10, fig.height = 12}
library(kableExtra)
library(rmarkdown)
library(dplyr)
library(tidyr)
library(ggplot2)

source("../../includes/mappings.R")

faculty <- params$tables[["inst_courses_w"]] %>% mutate(across(everything(),as.character))
faculty[is.na(faculty)] <- "0"
faculty <- faculty %>% rename(Instructor=INST_NAME, `Home Dept` = `Home Organization Desc`)
faculty$`Academic Title`[faculty$`Academic Title` == "0"] <- "--"
faculty$`Home Dept`[faculty$`Home Dept` == "0"] <- "--"

dept_fac_all_courses <- params$tables[["dept_fac_all_courses"]]

dept <- params$dept

title_str <- paste0(params$dept, " Workload Report")

knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE, dpi=200, fig.pos="H",fig.height=11,out.height="100%")
```



---
title: `r dept` Workload Report
subtitle: " "
---

- This report filters out courses like problems courses, independent studies, dissertation credits, etc. I have tried to be conservative with this, but it's possible that a legit course has been excluded here.
- Conversely, some of these kinds of courses (certain workshops, internships, etc) might be listed or counted here because the title was ambiguous.
- The listing for Irene Vasquez are wonky because apparently I gathered Summer 2023 data before the cross-listings data was added, with the result that the same Cultural Studies course is listed multiple times. I haven't seen this issue before, and it seems isolated to just Summer 2023.
- Split-level courses (grad and undergrad) are listed twice, unfortunately. This should be fixed in the next version of the reports.


<a id="top_anchor"></a>

```{r results="asis", echo=FALSE} 
if (!is.null(params$faculty)) {
  
cat("### Faculty Appointment Data\n")

  table <- kbl(params$faculty,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10)

  print(table)  

  cat("{[back to top](#top_anchor)}")
  }

```




```{r results="asis", echo=FALSE} 
if (!is.null(params$fac_list)) {
  
  cat("### Course count\n")

  core_faculty <- faculty %>% filter (Instructor %in% params$fac_list) %>%   ungroup() %>% select(-c(job_cat,`Home Dept`))
  
  table <- kbl(core_faculty,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 12)

  print(table)  
}

```
{[back to top](#top_anchor)}



### All courses faceted by instructor


```{r results="asis", echo=FALSE} 

names <- sort(unique(dept_fac_all_courses$INST_NAME))

for (name in names) {
  cat(paste0("#### ",name,"\n"))
  
  inst_courses <- dept_fac_all_courses %>% filter (INST_NAME == name) %>% ungroup()
  inst_courses <- inst_courses %>% select(-c(DEPT,INST_NAME,DEPARTMENT)) %>% arrange(TERM)
  
  table <- kbl(inst_courses,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10)
  
  print(table)
}

```

{[back to top](#top_anchor)}

<hr>

### Gen Ed Courses
```{r results="asis", echo=FALSE} 
  gen_ed <- dept_fac_all_courses %>% filter (GEN_ED == TRUE) %>%  
    select(TERM,CRSE_TITLE,INST_METHOD,INST_NAME,DEPT_ENRL,TOTAL_ENRL,XLIST_ENRL)
  
  table <- kbl(gen_ed,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd",       "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10)

  print(table)  

```


{[back to top](#top_anchor)}

<hr>

### Methodology
All data comes from UNM MyReports, specifically the Department Enrollment Status Report.
Some filtering and aggregating makes this report more readable, namely:

- filtering out courses like independent studies, dissertation hours, etc.
- compressing cross-listed courses into a single row to display both department and crosslist enrollments
- filtering out summer courses from the workload matrix

Job titles are taken from HRReports, but these are not fully normalized.
"--" as a value means there is no match in the A&S HR Report (ie their contract comes from another College).

{[back to top](#top_anchor)}

