---
title: "Workload Report"
output:
  html_document:
    df_print: paged
    toc: true
  pdf_document:
    fig_width: 7
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: yes
params:
  dept: "AFST"
  term: 202410
  faculty:
  fac_list: 1
  tables: 1
---

```{r setup, include=FALSE,  fig.width = 10, fig.height = 12}
library(kableExtra)
library(rmarkdown)
library(dplyr)
library(tidyr)
library(ggplot2)

source("../../includes/mappings.R")

faculty <- params$tables[["workload_w"]] %>% mutate(across(everything(),as.character))
faculty[is.na(faculty)] <- "0"
faculty <- faculty %>% rename(Instructor=INST_NAME, `Home Dept` = `Home Organization Desc`)
faculty$`Academic Title`[faculty$`Academic Title` == "0"] <- "--"
faculty$`Home Dept`[faculty$`Home Dept` == "0"] <- "--"

dept_fac_all_courses <- params$tables[["dept_fac_all_courses"]]
dept_courses <- params$tables[["dept_courses"]]
dept <- params$dept

title_str <- paste0(params$dept, " Workload Report")

knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE, dpi=200, fig.pos="H",fig.height=11,out.height="100%")
```



---
title: `r dept` Workload Report
subtitle: " "
---

<a id="top_anchor"></a>

```{r results="asis", echo=FALSE} 
if (!is.null(params$faculty)) {
  
cat("### Faculty Appointment Data\n")

  table <- kbl(params$faculty,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10)

  print(table)  

  cat("{[back to top](#top_anchor)}")
  }

```



### Recent Enrollments
- LINE: total enrollments across all courses; 
- BLACK DOTS: average enrollment per term
- RED DOTS: number of courses
```{r results="asis", echo=FALSE, fig.width = 8, fig.asp=.6,out.width="90%"} 
  enrl_summary <- params$table[["enrl_summary"]]
  
  ggplot(enrl_summary, aes(x=TERM)) + 
          geom_line(aes(y=ENRL),group=1) +
          theme(axis.text.x = element_text(angle = -45, hjust=0.05))
  
  ggplot(enrl_summary, aes(x=TERM)) + 
    geom_point(aes(y=AVG),group=2) + geom_line(aes(y=AVG),group=2) +
    geom_point(aes(y=NUM),group=3,color="red") + geom_line(aes(y=NUM),group=3,color="red") +
    theme(axis.text.x = element_text(angle = -45, hjust=0.05))
  
  
```
<br>



```{r results="asis", echo=FALSE} 
if (!is.null(params$fac_list)) {
  
cat("### ",dept," course count by ",dept," faculty per term\n")

  core_faculty <- faculty %>% filter (Instructor %in% params$fac_list) %>%   ungroup() %>% select(-c(job_cat,`Home Dept`))
  
  table <- kbl(core_faculty,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 12)

  print(table)  
}

```
{[back to top](#top_anchor)}

### `r dept` course count by external faculty
```{r results="asis", echo=FALSE} 
  aux_faculty <- faculty %>% filter (!Instructor %in% params$fac_list) %>% ungroup() %>% select(-c(job_cat))

  table <- kbl(aux_faculty,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 12)

  print(table)  

```

{[back to top](#top_anchor)}

<hr>

### `r dept` courses by `r dept` faculty
```{r results="asis", echo=FALSE} 


terms <- unique(dept_fac_all_courses$TERM)

for (term in terms) {
cat(paste0("#### ",term_text[which(num.labs == term)] ,"\n"))

  dept_fac_dept_courses <- dept_fac_all_courses %>% filter (DEPT == params$dept & TERM == term) %>%  ungroup() %>%
    arrange(TERM,INST_NAME)
  dept_fac_dept_courses <- dept_fac_dept_courses %>% select(-c(TERM,SUBJ_CRSE,DEPT,DEPARTMENT))
  
  table <- kbl(dept_fac_dept_courses,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10) %>% 
   scroll_box(width = "100%", height = "300px")


  print(table)  
}

```
{[back to top](#top_anchor)}
<hr>

### non-`r dept` courses by `r dept` faculty
```{r results="asis", echo=FALSE} 

terms <- unique(dept_fac_all_courses$TERM)

for (term in terms) {
cat(paste0("#### ",term_text[which(num.labs == term)] ,"\n"))
  
  dept_fac_other_courses <- dept_fac_all_courses %>% filter (DEPT != params$dept & TERM == term)%>% ungroup()
dept_fac_other_courses <- dept_fac_other_courses %>% select(-c(TERM,DEPT)) %>% arrange(INST_NAME)

  table <- kbl(dept_fac_other_courses,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),  latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10) %>% 
    scroll_box(width = "100%", height = "300px")

  print(table)  
}
```
{[back to top](#top_anchor)}

<hr>

### All courses by `r dept` faculty by instructor
```{r results="asis", echo=FALSE} 

names <- sort(unique(dept_fac_all_courses$INST_NAME))


for (name in names) {
cat(paste0("#### ",name,"\n"))

    inst_courses <- dept_fac_all_courses %>% filter (INST_NAME == name) %>% ungroup()
  inst_courses <- inst_courses %>% select(-c(DEPT,INST_NAME,DEPARTMENT)) %>% arrange(TERM)

  table <- kbl(inst_courses,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10)

  print(table)
}

```

{[back to top](#top_anchor)}

<hr>

### Gen Ed Courses
```{r results="asis", echo=FALSE} 
  gen_ed <- dept_courses %>% filter (gen_ed == TRUE) %>%  
    select(TERM,SUBJ,CRSE_TITLE,INST_METHOD,INST_NAME,`Academic Title`,ENROLLED,total_enrl,xl_enrl,reqs)
  
  table <- kbl(gen_ed,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd",       "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10)

  print(table)  

```

{[back to top](#top_anchor)}

<hr>

### Required Courses
```{r results="asis", echo=FALSE} 
  
  reqs <- dept_courses %>% filter (reqs != "") %>%  select(TERM,SUBJ,CRSE_TITLE,INST_METHOD,INST_NAME,`Academic Title`,ENROLLED,total_enrl,xl_enrl,reqs)
    
  table <- kbl(reqs,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10)

  print(table)  

```

{[back to top](#top_anchor)}

<hr>

### COURSES per job category
```{r results="asis", echo=FALSE, fig.width = 4, fig.asp=.6,out.width="50%"} 

course_pct <- dept_courses %>% group_by(`job_cat`) %>% summarize(COURSES=n(),`TERM MEAN`=COURSES/length(unique(dept_courses$TERM)))
course_pct <- course_pct %>% rename(TITLE = job_cat)

table <- kbl(course_pct %>% arrange(desc(`TERM MEAN`)),digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 12,position = "float_left")

print(table)

ggplot(course_pct, aes(x="", y=`TERM MEAN`, fill=TITLE)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + # remove background, grid, numeric labels
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))


```
<br>

{[back to top](#top_anchor)}

<hr>

### STUDENTS per job category
```{r results="asis", echo=FALSE, fig.width = 4, fig.asp=.6,out.width="50%"} 

  
  student_pct <- dept_courses %>% group_by(`job_cat`) %>% summarize(STUDENTS=sum(total_enrl),`TERM MEAN`=STUDENTS/length(unique(dept_courses$TERM)))
  student_pct <- student_pct %>% rename(TITLE = job_cat)

  table <- kbl(student_pct %>% arrange(desc(`TERM MEAN`)),digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 12,position = "float_left")
  
  print(table)

  ggplot(student_pct, aes(x="", y=`TERM MEAN`, fill=TITLE)) +
    geom_bar(stat="identity", width=1, color="white") +
    coord_polar("y", start=0) +
    theme_void() # remove background, grid, numeric labels
    
```

<br>

{[back to top](#top_anchor)}

<hr>

### All `r dept` courses by non-`r dept` faculty


```{r results="asis", echo=FALSE} 

  for (term in terms) {
    
    cat(paste0("#### ",term_text[which(num.labs == term)] ,"\n"))
    
    brief <- params$tables[["courses_brief"]]
    brief <- brief %>%  filter (!INST_NAME %in% params$fac_list & TERM == term) %>% select(-c(GEN_ED,REQS))  %>% arrange(TERM,INST_NAME)
    table <- kbl(brief,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 9)
    
    print(table)
  }
```

{[back to top](#top_anchor)}

<hr>

### Methodology
All data comes from UNM MyReports, specifically the Department Enrollment Status Report.
Some filtering and aggregating makes this report more readable, namely:

- filtering out courses like independent studies, dissertation hours, etc.
- compressing cross-listed courses into a single row to display both department and crosslist enrollments
- filtering out summer courses from the workload matrix

Job titles are taken from HRReports, but these are not fully normalized.
"--" as a value means there is no match in the A&S HR Report (ie their contract comes from another College).

{[back to top](#top_anchor)}

