---
title: "Course Report"
subtitle: " "
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false    
  pdf_print: paged
  pdf_document:
    fig_width: 7
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: yes
params:
  opt: 1
  course_data: 1
  rmd_file: 1
  output_dir_base: 1
  output_filename: 1
---

```{r setup, include=FALSE}
library(kableExtra)
library(rmarkdown)
library(DT)
library(dplyr)
library(tidyr)

opt <- params[["opt"]]
course <- opt[["course"]]
term <-opt[["term"]]

course_data <- params[["course_data"]]
enrls <- course_data[["enrls"]]
where_to_data <- course_data[["where_to"]]
where_from_data <- course_data[["where_from"]]
where_at_data <- course_data[["where_at"]]
agg_by_class <- course_data[["rollcall_by_class"]]
agg_by_major <- course_data[["rollcall_by_major"]]
grade_data <- course_data[["grades"]]
forecasts <- course_data[["forecasts"]]

flagged <- course_data[["reg_stats_flagged"]]
early_drops <- flagged[["early_drops"]]
late_drops <- flagged[["late_drops"]]
dips <- flagged[["dips"]]
bumps <- flagged[["bumps"]]

dt_opts <- list(scrollY="300", scrollX="100%", paging=FALSE)
dt_class <- 'cell-border stripe'

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.pos = "H", fig.width = 9)
```

```{css, echo=FALSE}

.tocify-header {
    text-indent: 10px;
    font-weight: bold;
    font-size: 120%
}


.tocify-subheader {
    text-indent: 20px;
    font-weight: normal;
    font-size: 80%
    line-height:80%
}

.tocify .list-group-item {
    font-size: 60%
    line-height:60%
}

@media print {

  #TOC { display: none; }

}
```

---
title: "`r course` "
subtitle: "Course Report"
---


### Filtering Options
```{r "filter options", results="asis"} 
cat("term: ", term)
cat("<br> part of term: ", opt$pt)
cat("<br> inst method: ", opt$im)
cat("<br> level: ", opt$level,"\n")
```


### FALL enrollments
```{r fall_enrl} 
cols <- c("CAMP", "COLLEGE", "TERM","enrolled", "cl_total", "sections","avg_size","avail","waiting", "dr_early", "dr_late","da_mean","squeeze")

# filter by term and course
enrl_fall <- enrls  %>% filter (SUBJ_CRSE == course ) %>% filter (substring(TERM,5,6) == 80) %>% select(cols)

enrl_spring <- enrls  %>% filter (SUBJ_CRSE == course) %>% filter (substring(TERM,5,6) == 10) %>% 
  ungroup()  %>% select(cols)

enrl_summer <- enrls  %>% filter (SUBJ_CRSE == course) %>% filter (substring(TERM,5,6) == 60) %>% 
  ungroup() %>% select(cols)

datatable(enrl_fall, options=dt_opts, class = dt_class)

# kbl(enrl_fall,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), position="left", full_width=F, font_size = 12)
```


### SPRING enrollments
```{r spring_enrl} 
datatable(enrl_spring, options=dt_opts, class = dt_class)

#table <- kbl(enrl_spring,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), position="left", full_width=F, font_size = 12)

```    


### SUMMER enrollments
```{r summer_enrl} 
datatable(enrl_summer, options=dt_opts, class = dt_class)

# table <- kbl(enrl_summer,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), position="left", full_width=F, font_size = 12)

```    


### More EARLY DROPS than usual
```{r early_drops} 
drops <- early_drops %>% arrange(term_type,`Academic Period Code`) 

datatable(early_drops, options=dt_opts, class = dt_class)

# table <- kbl(drops,digits=2)  %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
#                latex_options = c("striped","hold_position","condensed"), position="left", full_width=F, font_size = 12)
```


#### More LATE DROPS than usual
```{r late_drops} 
late_drops <- late_drops %>% arrange(term_type,`Academic Period Code`) 

datatable(late_drops, options=dt_opts, class = dt_class)

#table <- kbl(late_drops,digits=2)  %>%   
#  kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
#                latex_options = c("striped","hold_position","condensed"), position="left", full_width=F, font_size = 12) 
```


#### Bigger enrollment DIP than usual
```{r dips} 
dips <- dips %>% arrange(term_type,`Academic Period Code`) 
datatable(dips, options=dt_opts, class = dt_class)

# table <- kbl(dips,digits=2)  %>%   
#   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
#                 latex_options = c("striped","hold_position","condensed"), position="left", full_width=F, font_size = 12) 
```


####  Bigger enrollment BUMP than usual
```{r bumps} 
bumps <- bumps %>% arrange(term_type,`Academic Period Code`) 
datatable(bumps, options=dt_opts, class = dt_class)

# table <- kbl(bumps,digits=2)  %>%   
#   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
#                 latex_options = c("striped","hold_position","condensed"), position="left", full_width=F, font_size = 12) 
``` 


<div style="border:1px solid white; clear:both">
<div style="float:left; width:49%">

#### SPRING courses students come from
```{r where_spring} 
where_from_spring <- where_from_data %>% filter (to_crse == course & term_type =="spring") %>% 
  arrange (desc(avg_contrib)) %>% ungroup() %>% slice_head(n=5)

datatable(where_from_spring, options=dt_opts, class = dt_class)

# table <- kbl(where_from_spring,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10, position = "float_left")
```

</div>

#### FALL courses students come from

```{r where_fall} 
where_from_fall <- where_from_data %>% filter (to_crse == course & term_type == "fall") %>% 
  arrange (desc(avg_contrib)) %>% ungroup() %>% slice_head(n=5)

datatable(where_from_fall, options=dt_opts, class = dt_class)

# table <- kbl(where_from_fall,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"),  position="left", full_width=F, font_size = 10)
# 
# print(table)
```
</div>

<div style="border:1px solid white; clear:both">
<div style="float:left; width:49%">

#### FALL courses students go to
```{r where_to_fall} 
where_to_fall <- where_to_data %>% filter (from_crse == course & term_type == "fall") %>% 
  arrange (desc(avg_contrib)) %>% ungroup() %>% slice_head(n=5)

datatable(where_to_fall, options=dt_opts, class = dt_class)
# table <- kbl(where_to_fall,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10,  position = "float_left")
# print(table)
```
</div>


#### SPRING courses students go to
```{r where_to_spring} 
where_to_spring <- where_to_data %>% filter (from_crse == course & term_type =="spring") %>% 
  arrange (desc(avg_contrib)) %>% ungroup() %>% slice_head(n=5)

datatable(where_to_spring, options=dt_opts, class = dt_class)

# table <- kbl(where_to_spring,digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),latex_options = c("striped","hold_position","condensed"), position="left", full_width=F, font_size = 10)
# 
# print(table)
```
</div>


#### % classifications in FALL sections

```{r classifications, results='asis'} 
agg_by_class_fall <- agg_by_class %>% select(`Student Classification`,ends_with("80"))
agg_by_class_spring <- agg_by_class %>% select(`Student Classification`,ends_with("10"))
agg_by_class_summer <- agg_by_class %>% select(`Student Classification`,ends_with("60"))


if (ncol(agg_by_class_fall) > 3) {
  datatable(agg_by_class_fall, options=dt_opts, class = dt_class)
  # table <- kbl(agg_by_class_fall,digits=2)  %>%   
  #   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
  #                 latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10) %>% 
  #   scroll_box(width = "100%", height = "300px")
  # 
  # print(table)
}

if (ncol(agg_by_class_spring) > 3) {
    datatable(agg_by_class_fall, options=dt_opts, class = dt_class)

  cat(paste0("#### ","% of classifications in SPRING sections \n"))
  
  table <- kbl(agg_by_class_spring,digits=2)  %>%   
    kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
                  latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10) %>% 
    scroll_box(width = "100%", height = "300px")
  
  print(table)
}

if (ncol(agg_by_class_summer) > 3) {
  
  cat(paste0("#### ","% of classifications in SUMMER sections \n"))
  
  table <- kbl(agg_by_class_summer,digits=2)  %>%   
    kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
                  latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10) %>% 
    scroll_box(width = "100%", height = "300px")
  
  print(table)
}    
```


```{r majors} 
agg_by_major_fall <- agg_by_major  %>% select (Major,ends_with("80"))
agg_by_major_spring <- agg_by_major  %>% select (Major,ends_with("10"))
agg_by_major_summer <- agg_by_major  %>% select (Major,ends_with("60"))


if (ncol(agg_by_major_fall) > 3) {
  
  cat(paste0("#### ","% of majors in FALL sections \n"))
  
  table <- kbl(agg_by_major_fall,digits=2)  %>%   
    kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
                  latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10) %>% 
    scroll_box(width = "100%", height = "300px")
  
  
  print(table)
}


if (ncol(agg_by_major_spring) > 3) {
  
  cat(paste0("#### ","% of majors in SPRING sections \n"))
  
  
  table <- kbl(agg_by_major_spring,digits=2)  %>%   
    kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
                  latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10) %>% 
    scroll_box(width = "100%", height = "300px")
  
  
  print(table)
}

if (ncol(agg_by_major_summer) > 3) {
  
  
  cat(paste0("#### ","% of majors in SUMMER sections \n"))
  
  
  table <- kbl(agg_by_major_summer,digits=2)  %>%   
    kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
                  latex_options = c("striped","hold_position","condensed"), full_width=F, font_size = 10) %>% 
    scroll_box(width = "100%", height = "300px")
  
  
  print(table)
}

cat("\n")

```

#### Gradebook
```{r gradebook} 
grade_data <-  grade_data %>%  select(c(`Course Campus Code`, `Course College Code`, `Academic Period Code`,`DFW %`,8:ncol(grade_data)))

datatable(grade_data, options=dt_opts, class = dt_class)

# table <- kbl(grade_data,digits=2)  %>% 
#   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
#                 latex_options = c("striped","hold_position","condensed"), position="center", full_width=F, font_size = 10) %>% 
#   scroll_box(width = "100%", height = "300px")

# print(table)
```


```{r forecasts} 
cols <- c("CAMP", "TERM","SUBJ_CRSE","enrolled","cl_total", "sections", "avg_size", "avail","conduit","major", "pref_enrl_method","pref_cl_method","avg_enrl_accr","avg_cl_accr","rec_enrl_sections","diff_fr_prev_enrl","rec_cl_sections","diff_fr_prev_enrl")
forecast_filtered <- forecasts %>% select(cols) %>% arrange(CAMP,TERM,SUBJ_CRSE)

forecast_filtered_fall <- forecast_filtered %>% filter (substring(TERM,5,6) == 80)
forecast_filtered_spring <- forecast_filtered %>% filter (substring(TERM,5,6) == 10)
forecast_filtered_summer <- forecast_filtered %>% filter (substring(TERM,5,6) == 60)

```

#### FALL forecasts
```{r fall_forecasts} 
datatable(forecast_filtered_fall, options=dt_opts, class = dt_class)
# table <- kbl(forecast_filtered_fall,digits=2)  %>% 
#   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
#                 latex_options = c("striped","hold_position","condensed"), position="center", full_width=F, font_size = 11)

# print(table)
```

#### SPRING forecasts
```{r spring_forecasts} 
datatable(forecast_filtered_spring, options=dt_opts, class = dt_class)
# table <- kbl(forecast_filtered_spring,digits=2)  %>% 
#   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
#                 latex_options = c("striped","hold_position","condensed"), position="center", full_width=F, font_size = 11)
# 
# print(table)
```

#### SUMMER forecasts
```{r summer_forecasts} 
datatable(forecast_filtered_summer, options=dt_opts, class = dt_class)
# table <- kbl(forecast_filtered_summer,digits=2)  %>% 
#   kable_styling(bootstrap_options = c("striped", "hover", "condensd", "responsive"),
#                 latex_options = c("striped","hold_position","condensed"), position="center", full_width=F, font_size = 11)
# 
# print(table)
```

