---
title: "Seatfinder Report"
output:
  html_document:
    toc: false  
    toc_float:
      collapsed: false
      smooth_scroll: false    
  df_print: paged
  pdf_document:
    fig_width: 7
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: yes
params:
  term: 1
  opt: 1
  courses: 1
  term_start: 1
  term_end: 1
  tables: 1
  palette: 1
  rmd_file: 1
  output_dir_base: 1
  output_filename: 1
---

```{r setup, include=FALSE}
  library(kableExtra)
  library(rmarkdown)
  library(DT)

  knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE, dpi=200, out.height="40%")

  enrls <- params$tables[["enrls"]]

  gen_ed_summary <- params$tables[["gen_ed_summary"]]
  gen_ed_likely <- params$tables[["gen_ed_likely"]]
  course_type_summary <- params$tables[["course_type_summary"]]
  both_terms <- params$tables[["both_terms"]]
  prev_offered <- params$tables[["prev_offered"]]
  newly_offered <- params$tables[["newly_offered"]]


```

\newpage


### Filtering Options
```{r  results="asis", echo=FALSE} 
cat("term: ", opt$term)

cat("<br> part of term: ", opt$pt)

cat("<br> inst method: ", opt$im)

cat("<br> level: ", opt$level)

```


### Course Type Summary (compared to last year)
The last column is the difference between this term and last term. A positive number means more seats are available; negative means fewer.
```{r} 

datatable(course_type_summary,class = 'cell-border stripe')

# kbl(course_type_summary, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=T)



```

---


### Seats Available by Gen Ed Area
```{r} 
  gen_ed_summary <- gen_ed_summary %>% select(TERM,gen_ed_area,SUBJ_CRSE,CRSE_TITLE,PT,INST_METHOD,enrolled,sections,avg_size,avail,waiting,`DFW %`)
  
  colnames(gen_ed_summary) <- c("TERM","GE_AREA","SUBJ_CRSE","CRSE_TITLE", "PT", "METHOD", "ENRL", "SECTS","SECT_SIZE","AVAIL","WAIT","DFW %")

datatable(gen_ed_summary,class = 'cell-border stripe') 
# kbl(gen_ed_summary, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=T)
```

---

### Seats LIKELY Available by Gen Ed Area
These sections have 0 seats available, but also 0 enrolled. Likely the cap is 0 to delay enrollment.
```{r}
  gen_ed_likely <- gen_ed_likely %>% select(TERM,gen_ed_area,SUBJ_CRSE,CRSE_TITLE,PT,INST_METHOD,enrolled,sections,avg_size,avail,waiting,`DFW %`)
  
  colnames(gen_ed_likely) <- c("TERM","GE_AREA","SUBJ_CRSE","CRSE_TITLE", "PT", "METHOD", "ENRL", "SECTS","SECT_SIZE","AVAIL","WAIT","DFW %")

datatable(gen_ed_likely,class = 'cell-border stripe') 

# kbl(gen_ed_likely, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=T)
```

---

### Offered last year but not now
```{r} 

  prev_offered <- prev_offered %>% select(TERM,gen_ed_area,SUBJ_CRSE,CRSE_TITLE,PT,method,enrolled,sections,avg_size,avail,waiting)
  
  colnames(prev_offered) <- c("TERM","GE_AREA","SUBJ_CRSE","CRSE_TITLE", "PT", "METHOD", "ENRL", "SECTS","SECT_SIZE","AVAIL","WAIT")


datatable(prev_offered,class = 'cell-border stripe') 

# kbl(prev_offered, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=F)
```

---

### Offered now but not last year
```{r} 

  newly_offered <- newly_offered %>% select(TERM,gen_ed_area,SUBJ_CRSE,CRSE_TITLE,PT,method,enrolled,sections,avg_size,avail,waiting)
  
  colnames(newly_offered) <- c("TERM","GE_AREA","SUBJ_CRSE","CRSE_TITLE", "PT", "METHOD", "ENRL", "SECTS","SECT_SIZE","AVAIL","WAIT")


datatable(newly_offered,class = 'cell-border stripe') 
# kbl(newly_offered, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=F)
```

---

### Courses in common with last year
The last column is the difference between end-of-term enrollments this term and last year. A positive number means more seats are available; negative means fewer.
```{r} 
  both_terms <- both_terms %>% select(TERM,gen_ed_area,SUBJ_CRSE,CRSE_TITLE,PT,method,enrolled,sections,avg_size,avail,waiting, enrl_diff_from_last_year)
  
  colnames(both_terms) <- c("TERM","GE_AREA","SUBJ_CRSE","CRSE_TITLE", "PT", "METHOD", "ENRL", "SECTS","SECT_SIZE","AVAIL","WAIT","ENRL_DIFF")


datatable(both_terms,class = 'cell-border stripe') 

# kbl(both_terms, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=5)
```

