---
title: "Seatfinder Report"
output:
  html_document:
    toc: true  
    toc_float:
      collapsed: false
      smooth_scroll: false    
  df_print: paged
  pdf_document:
    fig_width: 7
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: yes
params:
  term: 1
  opt: 1
  courses: 1
  term_start: 1
  term_end: 1
  tables: 1
  palette: 1
  rmd_file: 1
  output_dir_base: 1
  output_filename: 1
---

```{r setup, include=FALSE}
  library(kableExtra)
  library(rmarkdown)
  knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE, dpi=200, out.height="40%")

  enrls <- params$tables[["enrls"]]

  gen_ed_summary <- params$tables[["gen_ed_summary"]]
  gen_ed_likely <- params$tables[["gen_ed_likely"]]
  course_type_summary <- params$tables[["course_type_summary"]]
  both_terms <- params$tables[["both_terms"]]
  prev_offered <- params$tables[["prev_offered"]]
  newly_offered <- params$tables[["newly_offered"]]


```

\newpage


### Filtering Options
```{r  results="asis", echo=FALSE} 
cat("term: ", opt$term)

cat("<br> part of term: ", opt$pt)

cat("<br> inst method: ", opt$im)

cat("<br> level: ", opt$level)
```



### Course Type Summary (compared to last year)
The last column is the difference between this term and last term. A positive number means more seats are available; negative means fewer.
```{r} 
kbl(course_type_summary, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=T)
```


### Seats Available by Gen Ed Area
```{r} 
kbl(gen_ed_summary, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=T)
```

### Seats LIKELY Available by Gen Ed Area
These sections have 0 seats available, but also 0 enrolled. Likely the cap is 0 to delay enrollment.
```{r} 
kbl(gen_ed_likely, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=T)
```


<div style="float:left">
### Offered last year but not now
```{r} 
kbl(prev_offered, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=F)
```
</div>

<div>
### Offered now but not last year
```{r} 
kbl(newly_offered, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=F)
```
</div>

<div style="float:none; clear:both">
### Courses in common with last year
The last column is the difference between this term and last term. A positive number means more seats are available; negative means fewer.
```{r} 
kbl(both_terms, digits=2)  %>%   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),latex_options = c("striped","hold_position","condensed","scale_down"), position="center", full_width=5)
```
</div>
